Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-24 ms.tex
changing efficiency description.

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
  0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
  0.1 & \eddrt \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6 in
\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. We assume that $\epsilon_{\rm rad}$ saturates to
0.1 at $\eddrt\simeq 0.1$. $\tilde{\dot{M}}$ correspond to the true
accretion rate (as opposed to the inflow rate on large scales--which
is generally what we mean by $\Mdot$).

>>>>

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
 2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
%   0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
%   0.1 & \eddrt \gsim 0.1
% \end{cases}
\label{eq:efficiency}
\end{align}

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6 in
\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. $\epsilon_{\rm rad}$ should saturate to 0.1 at
larger values of $\eddrt>0.01$, but such a black hole would certainly
be active and thermally unstable (and thus outside the scope of our
models). We note they $\eddrt<0.01$ for all of our models.
